Open Design 3D-Printable Adjustable Micropipette that meets ISO Standard for Accuracy.

### 2017-01-18 nature-comm-manuscript/manuscript.tex
submitted to nat comm

\documentclass{nature}

\usepackage{changepage}
%% make sure you have the nature.cls and naturemag.bst files where
%% LaTeX can find them

@@

\begin{abstract}
Scientific communities are drawn to the open source model as an increasingly utilitarian method to produce and share work.
Initially used as a means to develop freely available software, open source projects have been applied to hardware including scientific tools.
Increasing convenience of 3D printing has fueled the proliferation of open labware projects aiming to develop and share designs for scientific tools that can be produced in-house as cheap alternatives to commercial products.
We present our design of a micropipette that is assembled from 3D-printable parts and some hardware that works by actuating a disposable syringe to a user adjustable limit.
Graduations on the syringe are used to accurately adjust the set point to the desired volume.  
Our open design printed micropipette is assessed in comparison to a commercial pipette and meets ISO 8655 standards. (Add refs)
\end{abstract}

\section*{Introduction}
The open source development model, initially applied to software, is thriving in the development of open source scientific equipment due in part to increasing access of 3D printing\cite{Baden2015,Pearce2013}.
Additive manufacturing methods have existed for decades although the recent availability of inexpensive desktop printers\cite{MakerbotIndustries,RepRap} have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods\cite{Fullerton2014,Wittbrodt2013}.
Proliferation of free CAD software\cite{OpenScad,Blender,SketchUp,123D} and design sharing sites\cite{Thingiverse,NationalInstitutesofHealth,GrabCAD,GitHubInc} have also supported the growth and popularity of open designed parts and projects.
Open design 3D-printable lab equipment is an attractive idea because, like open source software, it allows free access to technology that is otherwise inaccessible due to proprietary and/or financial barriers. 
Open design tools create opportunity for scientists and educational programs in remote or resource limited areas to participate with inexpensive and easy to make tools\cite{Marzullo2012,Lang2011,Fobel2013,Baker2014,Cybulski2014}.
Open source development also enables the development of custom solutions to meet unique applications not met by commercial products that are shared freely and are user modifiable\cite{Fullerton2014,Pearce2012,Rankin2014,Sulkin2013,Dryden2015,DaCosta2014,Tek2008}.
Some advanced, noteworthy, open source scientific equipment include a PCR device\cite{ChaiBiotechnologiesInc2015}, and a two-photon microscope\cite{Rosenegger2014} although simple tools have potential to be impactful as they can serve a wider community.

Some simple and clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device, such as drill bit attachment designed to hold centrifuge tubes, allowing a dremel to be used as a centrifuge\cite{Garvey2009}.
Although this may make a rather crude centrifuge it may be an adequate solution for a fraction of the cost of a commercial centrifuge.
Other examples of open source research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, reactionware\cite{Symes2012,Kitson2012,Mathieson2013,Kitson2014}, microfluidics\cite{Brennan2015,Dragone2013} and the list continues to grow\cite{PlosCollections}.

@@

Air displacement pipettes use a piston operating principal to draw liquid into the pipette\cite{ISO8655}.
In a typical commercial pipette the piston is made to be gas-tight with a gasketed plunger inside a smooth barrel.
Consumer grade fused deposition modeling (FDM) printers are unable to build a smooth surface do to the formation of ridges that occur as each layer is deposited.
The ridges formed by FDM make it impractical to form a gas-tight seal between moving parts, even with a gasket.
Existing printable open-design micropipettes get around this limitation by stretching a membrane over one end of a printed tube, which when pressed causes the displacement.
The displacement membrane can be made from any elastic material such as a latex glove.
A few open design micropipettes exist including a popular one which, in addition to the printed parts, uses parts scavenged from a retractable pen\cite{Baden2014}.
Because there is no built in feature such as a readout for the user to set the displacement to a desired volume, this design requires the user to validate the volumes dispensed with a high precision scale.
Without verification with a scale the volumes dispensed can only be estimated based on calculations of the deflection of the membrane which is not a practical protocol.

We submit a new design whose major strength is the ability to adjust to any volume aided by the the built in scale
Our open design 3D-printable micropipette works by actuating a disposable syringe to a user adjustable set point.
This allows the user to set the pipette to a volume by reading the graduations on the syringe barrel.
We have also designed an adjusted graduation scale, to be used in place of the printed on scale, that corrects for the compressibility of air which allows the pipette to be set accurately.
Additionally our pipette offers a simplified assembly requiring no glue, tape, or permanent connections.

\begin{figure}
\caption{
{\bf CAD renderings of printable parts and cross-sections.} (A) The printed plunger part is a shaft pushes on the syringe plunger and slides in the printed body part. The printed plunger has a latching tongue and button which interfaces with the printed body part. (B) The printed body part holds the syringe and interfaces with the printed plunger part. The body part features the unlatching button and slots to hold the syringe in place by its flanges. The body part also has two cutouts in the top for the plunger button and for the hex nut and bolt.
}
\label{fig1}
\end{figure}

\begin{figure}
\caption{
{\bf CAD renderings of assembled pipette and function.} The pipette actuates the syringe to three positions. {\bf (A) The latched position.} When the plunger is pressed the pipette locks at this position. The tip is then placed in a liquid and the unlatching button is pressed to release the pipette back to the set position (B), drawing in liquid.  {\bf(B) The set position.} The position of the screw determines the total displacement that the plunger moves. The pipette is spring loaded to return to this position. {\bf (C) The blow-out position.} The fluid is transferred by pressing the plunger past the latched position to blow-out all the liquid. {\bf (D) Return to the latched position.} The pipette returns to the latched position ready to preform another transfer.
}
\label{fig2}
\end{figure}

\begin{figure}
\caption{
{\bf Photos of assembled pipettes.}  (A) Two assemblies of the pipette: the 100-1000 $\mu$L configuration (above) and the 30-300 $\mu$L configuration (below). (B) Close-up photo of the taped on scale for each of the syringes. 
}
\label{fig3}
\end{figure}

\section*{Results and Discussion}
Validation testing preformed with the existing graduations printed on the syringes did not meet the ISO standards.
According to ISO 8655 for a pipette with the maximum nominal volume of 1000 $\mu$L the systematic error cannot exceed 8 $\mu$L and the random error cannot exceed 3 $\mu$L.
For the maximum nominal volume of 300 $\mu$L the systemic error cannot exceed 4 $\mu$L and the random error cannot exceed 1.5 $\mu$L.
The commercial pipettes met these standards handily, but in our initial tests with our printed pipette we noticed large negative systematic error suggesting that we were missing a biasing factor. 
This error was exaggerated while transferring larger volumes.
After further investigation we realized that the graduations are intended to measure incompressible fluids within the syringe while we were using them to measure air while under vacuum.
Because the syringe graduations were used to measure the air under vacuum it could not be expected to serve as a 1:1 volume ratio of water that was pulled into the tip because under vacuum the air had expanded.
This explains the negative systematic error we were experiencing.
The water in the tip pulls on the air due to gravity which causes it to expand slightly but enough to make measuring with the graduation in this way inaccurate.
Our solution was to replace the built-in scale with a scale that accounted for the expansion.
Using the data from our initial testing we calculated a factor for the expansion and used that to make the new scale (\ref{S1_Fig} and \ref{S1_Fig}.)
With the new scale taped on the syringe our validation testing met the ISO 8655 standard.
Replacing the scale with our scale that accounts for the expansion corrected this effect. 
Our printed pipette with the adjusted scale meets ISO standards for accuracy and precision. (Table \ref{table3} and \ref{table4}).

@@

\begin{figure}
%%%\includegraphics{something} % this command will be ignored
\caption{Each figure legend should begin with a brief title for
the whole figure and continue with a short description of each
panel and the symbols used. For contributions with methods
sections, legends should not contain any details of methods, or
exceed 100 words (fewer than 500 words in total for the whole
paper). In contributions without methods sections, legends should
be fewer than 300 words (800 words or fewer in total for the whole
paper).}
\end{figure}

\section*{Another Section}

Sections can only be used in Articles.  Contributions should be
organized in the sequence: title, text, methods, references,
Supplementary Information line (if any), acknowledgements,
interest declaration, corresponding author line, tables, figure
legends.

Spelling must be British English (Oxford English Dictionary)

In addition, a cover letter needs to be written with the
following:
\begin{enumerate}
 \item A 100 word or less summary indicating on scientific grounds
why the paper should be considered for a wide-ranging journal like
\textsl{Nature} instead of a more narrowly focussed journal.
 \item A 100 word or less summary aimed at a non-scientific audience,
written at the level of a national newspaper.  It may be used for
\textsl{Nature}'s press release or other general publicity.
 \item The cover letter should state clearly what is included as the
submission, including number of figures, supporting manuscripts
and any Supplementary Information (specifying number of items and
format).
 \item The cover letter should also state the number of
words of text in the paper; the number of figures and parts of
figures (for example, 4 figures, comprising 16 separate panels in
total); a rough estimate of the desired final size of figures in
terms of number of pages; and a full current postal address,
telephone and fax numbers, and current e-mail address.
\end{enumerate}

See \textsl{Nature}'s website
(\texttt{http://www.nature.com/nature/submit/gta/index.html}) for
complete submission guidelines.

\begin{methods}
Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer (fig.~\ref{fig1}), in this case a Makerbot Replicator.
A 1 mL or 3 mL syringe twists to lock in the body part and is held into place by the syringe flanges.
The 30-300 $\mu$L configuration uses a 1 mL pipette and the 100-1000 $\mu$L configuration uses a 3 mL pipette.
The plunger part slides freely in the body part and actuates the syringe by pushing the thumb button (fig.~\ref{fig2}). 
The pipette is spring loaded towards a set point which is adjustable by a set-screw.
When the thumb button is pressed the system locks when it reaches the latched position, where it is ready to draw in fluid.
The plunger is held in place with a latching button design which is released with the unlatching button drawing in fluid.
The displacement is equal to the distance between the set position and the latched position.
The pipette can also be pressed past the latched position to `blow-out' the transferred fluid completely from the pipette tip.   
Additional materials required for assembly include two springs, a nut, a bolt and two washers.
Attempts to make a printable luer lock adapter for tips was abandoned as the surface of printed parts is too rough to make an air tight seal with the luer or pipette tip.
Instead, a combination of a barbed luer adapter and elastic tubing is used to attach the pipette tips.
Our printed pipette mimics commercial pipettes design, function, and user operation, making it intuitive to use.

Our pipette uses the air-displacement method, where a vacuum is applied to a pocket of air to draw liquid into the pipette.
As air is an compressible fluid, this pocket of air grows due to the weight of the liquid pulling on it.
Due to this effect the graduations on the syringe are not accurate, as they are designed for measuring liquid within the syringe.
At larger volumes this effect is more pronounced resulting in the volume measured being greater than the amount of liquid pulled into the syringe.
We remedied this by creating a new scale to account for the expansion.
The scale is printed on a transparency sheet and is taped onto the syringe for accurate measurements (See~\ref{S1_Fig} and \ref{S2_Fig}).

\subsection{Fabrication \& Assembly}
Two parts are printed (body.stl and plunger.stl) at normal resolution with rafts on a Makerbot Replicator.
A small amount of paraffin wax is applied to the screw to prevent slop from causing the set point to drift after each actuation.
The nut is sunk into the hex inset in the printed body part.
The bolt is threaded in from the top of the body into the nut.
Springs and washers are threaded onto the plunger of a 1 mL syringe for the 30-300 $\mu$L configuration.
Springs are placed inside a 3 mL syringe for the 100-1000 $\mu$L configuration.
The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly(fig.~\ref{fig3}).
Parts and cost are listed in Table~\ref{table1} and \ref{table2}.

@@

%% Put the bibliography here, most people will use BiBTeX in
%% which case the environment below should be replaced with
%% the \bibliography{} command.

% \begin{thebibliography}{1}
% \bibitem{dummy} Articles are restricted to 50 references, Letters
% to 30.
% \bibitem{dummyb} No compound references -- only one source per
% reference.
% \end{thebibliography}

\bibliographystyle{naturemag}
\bibliography{sample}

>>>>

\documentclass{naturegraphicx}

\usepackage{changepage}
\usepackage{graphicx}

%% make sure you have the nature.cls and naturemag.bst files where
%% LaTeX can find them

@@

\begin{abstract}
Scientific communities are drawn to the open source model as an increasingly utilitarian method to produce and share work.
Initially used as a means to develop freely available software, open source projects have been applied to hardware including scientific tools.
Increasing convenience of 3D printing has fueled the proliferation of open labware projects aiming to develop and share designs for scientific tools that can be produced in-house as cheap alternatives to commercial products.
We present our design of a micropipette that is assembled from 3D-printable parts and some hardware that works by actuating a disposable syringe to a user adjustable limit.
Graduations on the syringe are used to accurately adjust the set point to the desired volume.  
Our open design printed micropipette is assessed in comparison to a commercial pipette and meets ISO 8655 standards.
\end{abstract}

\section*{Introduction}
The open source development model, initially applied to software, is thriving in the development of open source scientific equipment due in part to increasing access of 3D printing\cite{Baden2015,Pearce2013}.
Additive manufacturing methods have existed for decades although the recent availability of inexpensive desktop printers\cite{MakerbotIndustries,RepRap} have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods\cite{Fullerton2014,Wittbrodt2013}.
Proliferation of free CAD software\cite{OpenScad,Blender,SketchUp,123D} and design sharing sites\cite{Thingiverse,NationalInstitutesofHealth,GrabCAD,GitHubInc} have also supported the growth and popularity of open designed parts and projects.
Open design 3D-printable lab equipment is an attractive idea because, like open source software, it allows free access to technology that is otherwise inaccessible due to proprietary and/or financial barriers. 
Open design tools create opportunity for scientists and educational programs in remote or resource limited areas to participate with inexpensive and easy to make tools\cite{Marzullo2012,Lang2011,Fobel2013,Baker2014,Cybulski2014,Bhamla2017}.
Open source development also enables the development of custom solutions to meet unique applications not met by commercial products that are shared freely and are user modifiable\cite{Fullerton2014,Pearce2012,Rankin2014,Sulkin2013,Dryden2015,DaCosta2014,Tek2008}.
Some advanced, noteworthy, open source scientific equipment include a PCR device\cite{ChaiBiotechnologiesInc2015}, a tissue scaffold printer\cite{Trachtenberg2014}, and a two-photon microscope\cite{Rosenegger2014} although simple tools have potential to be impactful as they can serve a wider community.

Some simple and clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device, such as drill bit attachment designed to hold centrifuge tubes, allowing a dremel to be used as a centrifuge\cite{Garvey2009}.
Although this may make a rather crude centrifuge it may be an adequate solution for a fraction of the cost of a commercial centrifuge.
Other examples of open source research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014,Patrick2015}, reactionware\cite{Symes2012,Kitson2012,Mathieson2013,Kitson2014}, microfluidics\cite{Brennan2015,Dragone2013} and the list continues to grow\cite{PlosCollections}.

@@

Air displacement pipettes use a piston operating principal to draw liquid into the pipette\cite{ISO8655}.
In a typical commercial pipette the piston is made to be gas-tight with a gasketed plunger inside a smooth barrel.
Consumer grade fused deposition modeling (FDM) printers are unable to build a smooth surface do to the formation of ridges that occur as each layer is deposited\cite{Takagishi2017}.
The ridges formed by FDM make it impractical to form a gas-tight seal between moving parts, even with a gasket.
Existing printable open-design micropipettes get around this limitation by stretching a membrane over one end of a printed tube, which when pressed causes the displacement.
The displacement membrane can be made from any elastic material such as a latex glove.
A few open design micropipettes exist including a popular one which, in addition to the printed parts, uses parts scavenged from a retractable pen\cite{Baden2014}.
Because there is no built in feature such as a readout for the user to set the displacement to a desired volume, this design requires the user to validate the volumes dispensed with a high precision scale.
Without verification with a scale the volumes dispensed can only be estimated based on calculations of the deflection of the membrane which is not a practical protocol.

We submit a new design whose major strength is the ability to adjust to any volume aided by the the built in scale.
Our open design 3D-printable micropipette works by actuating a disposable syringe to a user adjustable set point.
This allows the user to set the pipette to a volume by reading the graduations on the syringe barrel.
We have also designed an adjusted graduation scale, to be used in place of the printed on scale, that corrects for the compressibility of air which allows the pipette to be set accurately.
Additionally our pipette offers a simplified assembly requiring no glue, tape, or permanent connections.

\begin{figure}
\includegraphics[scale=0.4]{figure1.png} % this command will be ignored
\caption{
{\bf CAD renderings of printable parts and cross-sections.} (A) The printed plunger part is a shaft pushes on the syringe plunger and slides in the printed body part. The printed plunger has a latching tongue and button which interfaces with the printed body part. (B) The printed body part holds the syringe and interfaces with the printed plunger part. The body part features the unlatching button and slots to hold the syringe in place by its flanges. The body part also has two cutouts in the top for the plunger button and for the hex nut and bolt.
}
\label{fig1}
\end{figure}

\begin{figure}
\includegraphics[scale=0.4]{figure2.png} % this command will be ignored
\caption{
{\bf CAD renderings of assembled pipette and function.} The pipette actuates the syringe to three positions. {\bf (A) The latched position.} When the plunger is pressed the pipette locks at this position. The tip is then placed in a liquid and the unlatching button is pressed to release the pipette back to the set position (B), drawing in liquid.  {\bf(B) The set position.} The position of the screw determines the total displacement that the plunger moves. The pipette is spring loaded to return to this position. {\bf (C) The blow-out position.} The fluid is transferred by pressing the plunger past the latched position to blow-out all the liquid. {\bf (D) Return to the latched position.} The pipette returns to the latched position ready to preform another transfer.
}
\label{fig2}
\end{figure}

\begin{figure}
\includegraphics[scale=1]{figure3.png} % this command will be ignored
\caption{
{\bf Photos of assembled pipettes.}  (A) Two assemblies of the pipette: the 100-1000 $\mu$L configuration (above) and the 30-300 $\mu$L configuration (below). (B) Close-up photo of the taped on scale for each of the syringes. 
}
\label{fig3}
\end{figure}

\section*{Results and Discussion}
Validation testing preformed with the existing graduations printed on the syringes did not meet the ISO standards.
According to ISO 8655 for a pipette with the maximum nominal volume of 1000 $\mu$L the systematic error cannot exceed 8 $\mu$L and the random error cannot exceed 3 $\mu$L.
For the maximum nominal volume of 300 $\mu$L the systemic error cannot exceed 4 $\mu$L and the random error cannot exceed 1.5 $\mu$L.
The commercial pipettes met these standards handily, but in our initial tests with our printed pipette we noticed large negative systematic error suggesting that we were missing a biasing factor. 
This error was exaggerated while transferring larger volumes.
After further investigation we realized that the graduations are intended to measure incompressible fluids within the syringe while we were using them to measure air while under vacuum.
Because the syringe graduations were used to measure the air under vacuum it could not be expected to serve as a 1:1 volume ratio of water that was pulled into the tip because under vacuum the air had expanded.
This explains the negative systematic error we were experiencing.
The water in the tip pulls on the air due to gravity which causes it to expand slightly but enough to make measuring with the graduation in this way inaccurate.
Our solution was to replace the built-in scale with a scale that accounted for the expansion.
Using the data from our initial testing we calculated a factor for the expansion and used that to make the new scale (See SI Fig. 1 and SI Fig. 2). %\ref{S1_Fig} and \ref{S1_Fig}.
With the new scale taped on the syringe our validation testing met the ISO 8655 standard.
Replacing the scale with our scale that accounts for the expansion corrected this effect. 
Our printed pipette with the adjusted scale meets ISO standards for accuracy and precision. (Table \ref{table3} and \ref{table4}).

@@

\begin{methods}
Our printed pipette is designed to actuate a 1 mL or 3 mL syringe to a user set displacement.
The core of the design is two printed parts, the body and the plunger which are able to be printed on a consumer grade FDM printer (fig. 1~\ref{fig1}), in this case a Makerbot Replicator.
A 1 mL or 3 mL syringe twists to lock in the body part and is held into place by the syringe flanges.
The 30-300 $\mu$L configuration uses a 1 mL pipette and the 100-1000 $\mu$L configuration uses a 3 mL pipette.
The plunger part slides freely in the body part and actuates the syringe by pushing the thumb button (fig. 2~\ref{fig2}). 
The pipette is spring loaded towards a set point which is adjustable by a set-screw.
When the thumb button is pressed the system locks when it reaches the latched position, where it is ready to draw in fluid.
The plunger is held in place with a latching button design which is released with the unlatching button drawing in fluid.
The displacement is equal to the distance between the set position and the latched position.
The pipette can also be pressed past the latched position to `blow-out' the transferred fluid completely from the pipette tip.   
Additional materials required for assembly include two springs, a nut, a bolt and two washers.
Attempts to make a printable luer lock adapter for tips was abandoned as the surface of printed parts is too rough to make an air tight seal with the luer or pipette tip.
Instead, a combination of a barbed luer adapter and elastic tubing is used to attach the pipette tips.
Our printed pipette mimics commercial pipettes design, function, and user operation, making it intuitive to use.

Our pipette uses the air-displacement method, where a vacuum is applied to a pocket of air to draw liquid into the pipette.
As air is an compressible fluid, this pocket of air grows due to the weight of the liquid pulling on it.
Due to this effect the graduations on the syringe are not accurate, as they are designed for measuring liquid within the syringe.
At larger volumes this effect is more pronounced resulting in the volume measured being greater than the amount of liquid pulled into the syringe.
We remedied this by creating a new scale to account for the expansion.
The scale is printed on a transparency sheet and is taped onto the syringe for accurate measurements (See SI Fig. 1 and SI Fig. 2).% ~\ref{S1_Fig} and ~\ref{S2_Fig}).

\subsection{Fabrication \& Assembly}
Two parts are printed (body.stl and plunger.stl) at normal resolution with rafts on a Makerbot Replicator.
A small amount of paraffin wax is applied to the screw to prevent slop from causing the set point to drift after each actuation.
The nut is sunk into the hex inset in the printed body part.
The bolt is threaded in from the top of the body into the nut.
Springs and washers are threaded onto the plunger of a 1 mL syringe for the 30-300 $\mu$L configuration.
Springs are placed inside a 3 mL syringe for the 100-1000 $\mu$L configuration.
The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly (fig. 3~\ref{fig3}).
Parts and cost are listed in Table~\ref{table1} and \ref{table2}.

@@

%\bibliographystyle{naturemag}
%\bibliography{sample}

\begin{thebibliography}{10}
	\expandafter\ifx\csname url\endcsname\relax
	\def\url#1{\texttt{#1}}\fi
	\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
	\providecommand{\bibinfo}[2]{#2}
	\providecommand{\eprint}[2][]{\url{#2}}

	\bibitem{Baden2015}
	\bibinfo{author}{Baden, T.} \emph{et~al.}
	\newblock \bibinfo{title}{{Open Labware: 3-D Printing Your Own Lab Equipment}}.
	\newblock \emph{\bibinfo{journal}{PLOS Biology}} \textbf{\bibinfo{volume}{13}},
	\bibinfo{pages}{e1002086} (\bibinfo{year}{2015}).
	\newblock \urlprefix\url{http://dx.plos.org/10.1371/journal.pbio.1002086}.

	\bibitem{Pearce2013}
	\bibinfo{author}{Pearce, J.~M.}
	\newblock \emph{\bibinfo{title}{{Open-source Lab}}} (\bibinfo{year}{2013}).

	\bibitem{MakerbotIndustries}
	\bibinfo{author}{{Makerbot Industries}}.
	\newblock \bibinfo{title}{{Makerbot}} (\bibinfo{year}{2017}).
	\newblock \urlprefix\url{https://www.makerbot.com/}.

	\bibitem{RepRap}
	\bibinfo{author}{{RepRap Project}}.
	\newblock \bibinfo{title}{{RepRap}} (\bibinfo{year}{2017}).
	\newblock \urlprefix\url{reprap.org}.

	\bibitem{Fullerton2014}
	\bibinfo{author}{Fullerton, J.~N.}, \bibinfo{author}{Frodsham, G. C.~M.} \&
	\bibinfo{author}{Day, R.~M.}
	\newblock \bibinfo{title}{{3D printing for the many, not the few}}.
	\newblock \emph{\bibinfo{journal}{Nature Biotechnology}}
	\textbf{\bibinfo{volume}{32}}, \bibinfo{pages}{1086--1087}
	(\bibinfo{year}{2014}).
	\newblock \urlprefix\url{http://www.nature.com/doifinder/10.1038/nbt.3056}.

	\bibitem{Wittbrodt2013}
	\bibinfo{author}{Wittbrodt, B.} \emph{et~al.}
	\newblock \bibinfo{title}{{Life-cycle economic analysis of distributed
			manufacturing with open-source 3-D printers}}.
	\newblock \emph{\bibinfo{journal}{Mechatronics}} \textbf{\bibinfo{volume}{23}},
	\bibinfo{pages}{713--726} (\bibinfo{year}{2013}).
	\newblock
	\urlprefix\url{http://linkinghub.elsevier.com/retrieve/pii/S0957415813001153}.

	\bibitem{OpenScad}
	\bibinfo{author}{Kintel, M.}
	\newblock \bibinfo{title}{{OpenSCAD}} (\bibinfo{year}{2017}).
	\newblock \urlprefix\url{http://www.openscad.org/}.

	\bibitem{Blender}
	\bibinfo{author}{{Blender Foudation}}.
	\newblock \bibinfo{title}{{Blender}}  (\bibinfo{year}{2017}).
	\newblock \urlprefix\url{www.blender.org}.

	\bibitem{SketchUp}
	\bibinfo{author}{{Trimble Inc.}}
	\newblock \bibinfo{title}{{SketchUp}} (\bibinfo{year}{2016}).
	\newblock \urlprefix\url{www.sketchup.com}.

	\bibitem{123D}
	\bibinfo{author}{{Autodesk Inc.}}
	\newblock \bibinfo{title}{{Autodesk 123D}} (\bibinfo{year}{2017}).
	\newblock \urlprefix\url{www.123dapp.com}.

	\bibitem{Thingiverse}
	\bibinfo{author}{{Makerbot Industries}}.
	\newblock \bibinfo{title}{{Thingiverse}} (\bibinfo{year}{2017}).
	\newblock \urlprefix\url{https://www.thingiverse.com/}.

	\bibitem{NationalInstitutesofHealth}
	\bibinfo{author}{{National Institutes of Health}}.
	\newblock \bibinfo{title}{{NIH 3D Print Exchange}}  (\bibinfo{year}{2017}).
	\newblock \urlprefix\url{http://3dprint.nih.gov/}.

	\bibitem{GrabCAD}
	\bibinfo{author}{Stratasys}.
	\newblock \bibinfo{title}{{GrabCAD}}.
	\newblock \urlprefix\url{https://grabcad.com/}.

	\bibitem{GitHubInc}
	\bibinfo{author}{{GitHub Inc.}}
	\newblock \bibinfo{title}{{GitHub}}  (\bibinfo{year}{2017}).
	\newblock \urlprefix\url{https://github.com/}.

	\bibitem{Marzullo2012}
	\bibinfo{author}{Marzullo, T.~C.} \& \bibinfo{author}{Gage, G.~J.}
	\newblock \bibinfo{title}{{The SpikerBox: A Low Cost, Open-Source BioAmplifier
			for Increasing Public Participation in Neuroscience Inquiry}}.
	\newblock \emph{\bibinfo{journal}{PLoS ONE}} \textbf{\bibinfo{volume}{7}},
	\bibinfo{pages}{e30837} (\bibinfo{year}{2012}).
	\newblock \urlprefix\url{http://dx.plos.org/10.1371/journal.pone.0030837}.

	\bibitem{Lang2011}
	\bibinfo{author}{Lang, T.}
	\newblock \bibinfo{title}{{Advancing global health research through digital
			technology and sharing data.}}
	\newblock \emph{\bibinfo{journal}{Science (New York, N.Y.)}}
	\textbf{\bibinfo{volume}{331}}, \bibinfo{pages}{714--717}
	(\bibinfo{year}{2011}).

	\bibitem{Fobel2013}
	\bibinfo{author}{Fobel, R.}, \bibinfo{author}{Fobel, C.} \&
	\bibinfo{author}{Wheeler, A.~R.}
	\newblock \bibinfo{title}{{DropBot: An open-source digital microfluidic control
			system with precise control of electrostatic driving force and instantaneous
			drop velocity measurement}}.
	\newblock \emph{\bibinfo{journal}{Applied Physics Letters}}
	\textbf{\bibinfo{volume}{102}}, \bibinfo{pages}{1--5} (\bibinfo{year}{2013}).

	\bibitem{Baker2014}
	\bibinfo{author}{Baker, E.}
	\newblock \bibinfo{title}{{Open source data logger for low-cost environmental
			monitoring.}}
	\newblock \emph{\bibinfo{journal}{Biodiversity data journal}}
	\bibinfo{pages}{e1059} (\bibinfo{year}{2014}).
	\newblock
	\urlprefix\url{http://www.pubmedcentral.nih.gov/articlerender.fcgi?artid=4030251{\&}tool=pmcentrez{\&}rendertype=abstract}.

	\bibitem{Cybulski2014}
	\bibinfo{author}{Cybulski, J.~S.}, \bibinfo{author}{Clements, J.} \&
	\bibinfo{author}{Prakash, M.}
	\newblock \bibinfo{title}{{Foldscope: origami-based paper microscope.}}
	\newblock \emph{\bibinfo{journal}{PloS one}} \textbf{\bibinfo{volume}{9}},
	\bibinfo{pages}{e98781} (\bibinfo{year}{2014}).
	\newblock
	\urlprefix\url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0098781}.
	\newblock \eprint{1403.1211}.

	\bibitem{Bhamla2017}
	\bibinfo{author}{Bhamla, M.~S.} \emph{et~al.}
	\newblock \bibinfo{title}{{Hand-powered ultralow-cost paper centrifuge}}.
	\newblock \emph{\bibinfo{journal}{Nature Biomedical Engineering}}
	\textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{0009} (\bibinfo{year}{2017}).
	\newblock \urlprefix\url{http://www.nature.com/articles/s41551-016-0009}.

	\bibitem{Pearce2012}
	\bibinfo{author}{Pearce, J.~M.}
	\newblock \bibinfo{title}{{Building Research Equipment with Free, Open-Source
			Hardware}}.
	\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{337}},
	\bibinfo{pages}{1303--1304} (\bibinfo{year}{2012}).
	\newblock
	\urlprefix\url{citeulike-article-id:11241059{\%}5Cnhttp://dx.doi.org/10.1126/science.1226328
		http://www.ncbi.nlm.nih.gov/pubmed/22984060
		http://www.sciencemag.org/cgi/doi/10.1126/science.1228183}.

	\bibitem{Rankin2014}
	\bibinfo{author}{Rankin, T.~M.} \emph{et~al.}
	\newblock \bibinfo{title}{{Three-dimensional printing surgical instruments: are
			we there yet?}}
	\newblock \emph{\bibinfo{journal}{Journal of Surgical Research}}
	\textbf{\bibinfo{volume}{189}}, \bibinfo{pages}{193--197}
	(\bibinfo{year}{2014}).
	\newblock
	\urlprefix\url{http://linkinghub.elsevier.com/retrieve/pii/S0022480414001644}.

	\bibitem{Sulkin2013}
	\bibinfo{author}{Sulkin, M.~S.} \emph{et~al.}
	\newblock \bibinfo{title}{{Three-dimensional printing physiology laboratory
			technology}}.
	\newblock \emph{\bibinfo{journal}{AJP: Heart and Circulatory Physiology}}
	\textbf{\bibinfo{volume}{305}}, \bibinfo{pages}{H1569--H1573}
	(\bibinfo{year}{2013}).
	\newblock
	\urlprefix\url{http://ajpheart.physiology.org/cgi/doi/10.1152/ajpheart.00599.2013}.

	\bibitem{Dryden2015}
	\bibinfo{author}{Dryden, M. D.~M.} \& \bibinfo{author}{Wheeler, A.~R.}
	\newblock \bibinfo{title}{{DStat: A versatile, open-source potentiostat for
			electroanalysis and integration}}.
	\newblock \emph{\bibinfo{journal}{PLoS ONE}} \textbf{\bibinfo{volume}{10}},
	\bibinfo{pages}{1--17} (\bibinfo{year}{2015}).
	\newblock \urlprefix\url{http://dx.doi.org/10.1371/journal.pone.0140349}.

	\bibitem{DaCosta2014}
	\bibinfo{author}{da~Costa, E.~T.} \emph{et~al.}
	\newblock \bibinfo{title}{{Getting started with open-hardware: Development and
			control of microfluidic devices}}.
	\newblock \emph{\bibinfo{journal}{Electrophoresis}}
	\textbf{\bibinfo{volume}{35}}, \bibinfo{pages}{2370--2377}
	(\bibinfo{year}{2014}).

	\bibitem{Tek2008}
	\bibinfo{author}{Tek, P.} \emph{et~al.}
	\newblock \bibinfo{title}{{Rapid prototyping for neuroscience and neural
			engineering}}.
	\newblock \emph{\bibinfo{journal}{Journal of Neuroscience Methods}}
	\textbf{\bibinfo{volume}{172}}, \bibinfo{pages}{263--269}
	(\bibinfo{year}{2008}).

	\bibitem{ChaiBiotechnologiesInc2015}
	\bibinfo{author}{{Chai Biotechnologies Inc}}.
	\newblock \bibinfo{title}{{Open PCR}} (\bibinfo{year}{2017}).
	\newblock \urlprefix\url{http://openpcr.org/}.

	\bibitem{Trachtenberg2014}
	\bibinfo{author}{Trachtenberg, J.~E.} \emph{et~al.}
	\newblock \bibinfo{title}{{Open-source three-dimensional printing of
			biodegradable polymer scaffolds for tissue engineering}}.
	\newblock \emph{\bibinfo{journal}{Journal of Biomedical Materials Research -
			Part A}} \textbf{\bibinfo{volume}{102}}, \bibinfo{pages}{4326--4335}
	(\bibinfo{year}{2014}).

	\bibitem{Rosenegger2014}
	\bibinfo{author}{Rosenegger, D.~G.}, \bibinfo{author}{Tran, C. H.~T.},
	\bibinfo{author}{LeDue, J.}, \bibinfo{author}{Zhou, N.} \&
	\bibinfo{author}{Gordon, G.~R.}
	\newblock \bibinfo{title}{{A High Performance, Cost-Effective, Open-Source
			Microscope for Scanning Two-Photon Microscopy that Is Modular and Readily
			Adaptable}}.
	\newblock \emph{\bibinfo{journal}{PLoS ONE}} \textbf{\bibinfo{volume}{9}},
	\bibinfo{pages}{e110475} (\bibinfo{year}{2014}).
	\newblock \urlprefix\url{http://dx.plos.org/10.1371/journal.pone.0110475}.

	\bibitem{Garvey2009}
	\bibinfo{author}{Garvey, C.}
	\newblock \bibinfo{title}{{DremelFuge}} (\bibinfo{year}{2009}).
	\newblock \urlprefix\url{https://www.thingiverse.com/thing:1483}.
